---
title: "Plant Growth"
output: 
    pdf_document:
        toc: true
fontsize: 10pt
---

```{r, echo = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, cache = TRUE)
```

```{r}
library(tidyverse)
```

# Part 1

1. [Plant Growth Experiment] This problem will give you practice with tidying a
dataset so that it can be easily visualized. The data describe the height of
several plants measured every 7 days. The plants have been treated with
different amounts of a growth stimulant. The first few rows are printed below --
`height.x` denotes the height of the plant on day `x`.
    
    ```{r}
    plants <- read_csv("https://uwmadison.box.com/shared/static/qg9gwk2ldjdtcmmmiropcunf34ddonya.csv")
    plants
    ```
     
    a. Propose an alternative arrangement of rows and columns that conforms to the
    tidy data principle.
    
# Part 2
```{r}
plants2 <- plants |>
pivot_longer(
    cols= starts_with("height"),
    names_to="time",
    values_to="height", 
    names_prefix = c("height.")
) |>
mutate(time = as.numeric(time))



#plant_df$time <- as.integer(plant_df$time)

#plants2

```

    b. Implement your proposed arrangement from part (a).
    
    c. Using the dataset from (b), design and implement a visualization showing the
    growth of the plants over time according to different treatments. \

```{r}
plants2

ggplot(plants2) +
    geom_line(aes(time, height, col =treatment, group = interaction(plantid,treatment)))+
    facet_wrap((~ treatment))
```



