---
title: "Demos"
output: html_document
---

```{r}
library(tidyverse)
theme_set(theme_minimal())
```

### Exercise Review [Student Exercise Analysis]

The data
[here](https://raw.githubusercontent.com/krisrs1128/stat679_code/main/examples/week1/formulating_questions.csv)
give an (anonymized) summary of responses to the [Formulating Questions]
exercise, given by students in Stat 679 / 992 in Fall 2022. It describes the
dataset topic, its source, the submitted visualization type, and the software
used to create it.

a. What types of topics seem to interest students in this class?

```{r}
responses <- read_csv("https://raw.githubusercontent.com/krisrs1128/stat679_code/main/examples/week1/formulating_questions.csv")
head(responses)

counts <- responses %>%
  count(category)

ggplot(counts) +
  geom_col(aes(n, reorder(category, n))) +
  theme(
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14)
  ) +
  labs(x = "Number of Submissions", y = "Category")
```

b. What types of visualization techniques and software to students seem most
familiar with? How should teaching be adapted to reflect this?

```{r}
responses %>%
  count(visualization, package) %>%
  ggplot() +
  geom_tile(aes(reorder(package, -n), reorder(visualization, -n), fill = n)) +
  scale_fill_distiller(direction = 1) +
  theme(panel.grid = element_blank())
```

c. When were submissions being made? Are the in-class exercises actually being
solved in class?

```{r}
library(lubridate)
responses %>%
  count(submission_date) %>%
  mutate(submission_date = as_date(submission_date, format = "%m/%d/%y")) %>%
  ggplot() +
  geom_point(aes(submission_date, 0, size = n))
```

### Code Demo [City Temperatures]

Let's create versions of Figure 2.3 and 2.4 from the
[reading](https://clauswilke.com/dataviz/aesthetic-mapping.html) this week. The
command below reads in the data. We've filtered to a slightly different set of
cities (Barrow is in Alaska, Honolulu is in Hawaii), but we should still be able
to study changes in temperature over time.

```{r}
temperature <- read_csv("https://raw.githubusercontent.com/krisrs1128/stat479_s22/main/data/temperatures.csv")
```

a. Make a version of Figure 2.3 using a line mark (`geom_line`). Make at
least one customization of the theme to make the plot more similar to the
version in Figure 2.3. _Hint: To group the lines by city, use the `group = ` aesthetic mapping._

```{r}
ggplot(temperature) +
  geom_line(aes(date, temperature, col = city, group = city), size = 2) +
  scale_x_date(date_labels = "%B")
```


b. Using the `group_by` + `summarise` pattern, compute the mean temperature
for each month in each city.

c. Using the data generated in (b), Make a version of Figure 2.4 using a
tile mark (`geom_tile`). Try either (i) adding the `scale_fill_viridis_c(option =
"magma")` scale to match the color scheme from the reading or (ii) adding
`coord_fixed()` to make sure the marks are squares, not rectangles.

```{r}
temperature %>%
  group_by(city, month) %>%
  summarise(mean_temp = mean(temperature)) %>%
  ggplot() +
  geom_tile(aes(month, reorder(city, mean_temp), fill = mean_temp)) +
  scale_fill_viridis_c(option = "magma")
```

d. Compare and contrast the two displays. What types of comparisons are
easier to make / what patterns are most readily visible using Figure 2.3 vs.
Figure 2.4, and vice versa?
