---
title: "Plant Growth"
output: html_document
---

```{r}
library(tidyverse)
```

1. [Plant Growth Experiment] This problem will give you practice with tidying a
dataset so that it can be easily visualized. The data describe the height of
several plants measured every 7 days. The plants have been treated with
different amounts of a growth stimulant. The first few rows are printed below --
`height.x` denotes the height of the plant on day `x`.
    
    ```{r}
    plants <- read_csv("https://uwmadison.box.com/shared/static/qg9gwk2ldjdtcmmmiropcunf34ddonya.csv")
    ```
    
    a. Propose an alternative arrangement of rows and columns that conforms to the
    tidy data principle.
    
```{r}
head(plants)

plants_reshaped <- plants %>%
  pivot_longer(starts_with("height"), names_to = "day", values_to = "value") %>%
  separate(day, c("tmp", "day"), convert = TRUE) %>%
  select(-tmp)
```
    
    b. Implement your proposed arrangement from part (a).
    
    c. Using the dataset from (b), design and implement a visualization showing the
    growth of the plants over time according to different treatments.
    
    
    
```{r}
ggplot(plants_reshaped) +
  geom_line(aes(day, value, col = treatment, group = interaction(treatment, plantid))) +
  facet_wrap(~ treatment)
```
    
    