---
title: "STAT 479: MIDTERM 1"
geometry: margin=2cm
output:
  pdf_document:
    keep_tex: true
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(tidyverse)
opts_chunk$set(cache = TRUE, message = FALSE, warning = FALSE, echo = TRUE, include = TRUE)
options(width = 200)
th <- theme_minimal() + 
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "#f7f7f7"),
    panel.border = element_rect(fill = NA, color = "#0c0c0c", size = 0.6),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.position = "bottom"
  )
theme_set(th)
```

* This exam lasts from 1:20 - 2:10pm on February 28, 2022. There are 7
questions.
* This exam is closed notes and closed computer.
* You may use a 1-page cheat sheet (8.5 x 11in or A4 size). You may use both
sides, but the cheat sheet must be handwritten.
* If you need extra space, you may write on the back of the page. Please
indicate somewhere that your answer continues.
* The instructors will only be able to answer clarifying questions during the
exam. They will be sitting at the back of the room.

| Question | Q1 | Q2 | Q3 | Q4 | Q5 | Q6 | Q7 | Total |
| ---- | -- | -- | -- | -- | -- | -- | -- | -- |
| Score |  |  |  |  |  |  |  |  | |
| Possible | 2 | 2 | 4 | 4 | 6 | 6 | 6 | 30 |


### Q1 [2 points]

Circle all the true statements for compound and faceted figures.

a. Whenever possible, each panel in a faceted plot should be made to have its
own $y$-axis scale.
b. When using the `patchwork` package, two plots `p1` and `p2` can be placed
side-by-side using `p1 / p2`.
c. When using the `patchwork` package, the `plot_layout` function can be used to collect legends.
d. Relative to interactively filtered displays, faceted plots are less taxing on the reader's memory.
  
### Q2 [2 points]

The code below generates a histogram of prices for a subset of items sold at
Ikea, a furniture outlet.

```{r, fig.height = 1.5, fig.width = 6}
ikea <- read_csv("https://uwmadison.box.com/shared/static/iat31h1wjg7abhd2889cput7k264bdzd.csv") %>%
  filter(category %in% c("Tables", "Bookcases", "Beds", "Cabinets", "Sofas", "Wardrobes"))
ggplot(ikea) +
  geom_histogram(aes(log(price)))
```

The four plots (i - iv) are generated by faceting this base plot by furniture
category (the variable `category`). On the blank lines below, put the number of
the plot that matches the corresponding faceting command, or leave the line
empty if the corresponding plot does not appear.

  a. `facet_grid(category ~ .)`

  b. `facet_wrap(~ category)`

  c. `facet_wrap(~ category, scales = "free_y")`

  d. `facet_wrap(~ category, axes = "separate")`

  e. `facet_wrap(~ reorder(category, price))`

```{r, echo = FALSE, fig.height = 9, fig.width = 12}
p <- ggplot(ikea) +
  geom_histogram(aes(log(price)), bins = 14)

ikea_list <- list()
ikea_list[[1]] <- p + facet_wrap(~ category, ncol = 4) + ggtitle("(i)")
ikea_list[[2]] <- p + facet_grid(category ~ .) +
  theme(strip.text.y = element_text(angle = 0)) +
  ggtitle("(ii)")
ikea_list[[3]] <- p + facet_wrap(~ category, scales = "free_y", ncol = 4) +
  ggtitle("(iii)")
ikea_list[[4]] <- p + facet_wrap(~ reorder(category, price), ncol = 4) +
  ggtitle("(iv)")

library(patchwork)
(ikea_list[[1]] + ikea_list[[2]]) /
(ikea_list[[3]] + ikea_list[[4]])
```


### Q3 [4 points]

Consider the sales data below.
        
```{r, echo = FALSE}
sales <- data.frame(
  region =  c('A', 'A', 'A', 'A', 'B', 'B', 'B', 'B'),
  quarter = c('Q1', 'Q2', 'Q3', 'Q4', 'Q1', 'Q2', 'Q3', 'Q4'),
  sales = c(6, 5, 3, 2, 4, 8, 2, 6)
)
sales
```

a. [2 points] Provide code to compute the total sales for each quarter, across both regions.
The result should look like the table below.
  
b. [2 points] Provide code to compute the proportion of each quarter's sales that came
from each region. The result should look like the table below.

### Q4 [4 points]

Consider the `reactive()` and `observeEvent()` functions implemented by the
`shiny` package. What are common use cases for the two functions? Be as specific
as possible.

`reactive()`

  * Often used to remove code duplication across `render*` contexts
  
  * Often used to create filtered / updated datasets from one set of user inputs
  to another, before passing them to tables or plots.
  
  * Often used to perform more intensive computations that are shared across
  several outputs
  
  * Often used to trim redundancies in reactive graphs
  
`observeEvent()`

  * Often used to modify reactive values.
  
  * Often used for graphical queries, to modify distances with click inputs or
  selections with linked brushing inputs.
  
  * Often used to execute code on `input` changes that are not necessary for
  specific rendered changes. For example, can be used to print messages or
  modify style elements without requiring new render calls.
  
### Q5 [6 points]

Below, we provide three approaches to visualizing species abundance over time in
an antibiotics dataset.

```{r}
antibiotic <- read_csv("https://uwmadison.box.com/shared/static/5jmd9pku62291ek20lioevsw1c588ahx.csv")
antibiotic
```

For each approach, describe,

  * One type of visual comparison for which the visualization is well-suited.
  
  * One type of visual comparison for which the visualization is poorly-suited.
  
Make sure to explain your reasoning.

a. [1.5 points] Approach 1
```{r, echo = FALSE, out.width = "0.55\\textwidth"}
ggplot(antibiotic, aes(x = time)) +
  geom_line(aes(y = svalue), size = 1.2) +
  geom_point(aes(y = value, col = antibiotic), size = 0.5, alpha = 0.8) +
  facet_grid(species ~ ind, scale = "free_y") +
  scale_color_brewer(palette = "Set2") +
  theme(strip.text.y = element_text(angle = 0))
```

b. [1.5 points] Approach 2
```{r, echo = FALSE, out.width = "0.55\\textwidth"}
ggplot(antibiotic) +
  geom_tile(aes(time, ind, fill = value)) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_fill_distiller(direction = 1) +
  facet_grid(species ~ .) +
  theme(strip.text.y = element_text(angle = 0))
```

c. [1.5 points] Approach 3
```{r, echo = FALSE, out.width = "0.55\\textwidth"}
ggplot(antibiotic) +
  geom_line(aes(time, svalue, col = species, group = interaction(species, ind))) +
  facet_grid(ind ~ .) +
  scale_color_brewer(palette = "Set2")
```

d. [1.5 points] Sketch code that could be used to make one of the three visualizations above.


### Q6 [6 points]

The following questions refer to the NYC flights dataset. The first few lines
are printed below.

```{r}
library(nycflights13)
flights %>% select(carrier, air_time, distance)
```

a. [3 points] Provide code to create a new column giving the average speed of
the flight: $\texttt{speed} := \frac{\texttt{distance}}{\texttt{air\_time}}$.

b. [3 points] Is there a large variation in flight speed across carriers? Design
and sketch code for a visualization that could be used to answer this
question (you may assume the output of (a)).

### Q7 [6 points]

The code below sets up a Shiny app for interactively visualizing athlete weight
and heights in the 2012 London Olympics. We would like to have an interactive
scatterplot of `Weight` vs. `Height, cm` that updates which points (athletes)
are highlighted depending on sports have been selected by a dropdown menu. Code
for generating the scatterplot is provided in the function `scatterplot`.

```{r}
library(shiny)
library(tidyverse)
olympics <- read_csv("https://uwmadison.box.com/shared/static/rzw8h2x6dp5693gdbpgxaf2koqijo12l.csv")

#' Scatterplot with highlighted points
#' 
#' Assumes a column in df called "selected" saying whether points should be
#' larger / darker
scatterplot <- function(df) {
  ggplot(df) +
    geom_point(
      aes(Weight, `Height, cm`, 
          alpha = as.numeric(selected),
          size = as.numeric(selected))
      ) +
    scale_alpha(range = c(0.05, .8)) +
    scale_size(range = c(0.1, 1))
}

ui <- fluidPage(
  selectInput("dropdown", "Select a Sport", choices = unique(olympics$Sport), multiple = TRUE),
  plotOutput("scatterplot")
)

server <- function(input, output) {
  ### fill this in...
}
```

a. [3 points] Provide server code which would allow the scatterplot to update
the highlighted athletes depending on the currently selected sports.

b. [3 points] We have been asked to also print a table of the selected athletes.
Assume the UI has the form,
    
    ```{r}
    ui <- fluidPage(
      selectInput("dropdown", "Select a Sport", choices = unique(olympics$Sport), multiple = TRUE),
      plotOutput("scatterplot"),
      dataTableOutput("table") 
    )
    ```
    
    Describe changes to your solution to (a) to meet the new requirements. How
    would you minimize code duplication? Be as specific as possible.
      
