---
title: ""
output: html_document
---

```{r}
library(tidyverse)
library(tidymodels)
theme_set(theme_bw())
set.seed(1234)
```
    
This problem will study a dataset from MIT's [living wage
calculator](https://livingwage.mit.edu/). Each row in this
[dataset](https://raw.githubusercontent.com/krisrs1128/stat479_s22/main/_slides/week10/exercises/living_wages.csv)
gives living wages for state capitals within the continental US. Since living
wages depend on a personal situation (e.g., number of children), this dataset is
high-dimensional. The interpretation of each column is 
[here](https://raw.githubusercontent.com/krisrs1128/stat479_s22/main/_slides/week10/exercises/living_wages_lookup.csv).


```{r}
living_wages <- read_csv("https://raw.githubusercontent.com/krisrs1128/stat992_f23/main/activities/week12/living_wages.csv")
lookup <- read_csv("https://raw.githubusercontent.com/krisrs1128/stat992_f23/main/activities/week12/living_wages_lookup.csv")
living_wages
```

a. Define a tidymodels `recipe` that normalizes all city features and
specifies that PCA should be performed.

```{r}
pca_recipe <- recipe(~ ., living_wages) |>
  update_role(state_territory:city, new_role = "id") |>
  step_normalize(all_predictors()) |>
  step_pca(all_predictors())

pca_prep <- prep(pca_recipe)
```


b. Visualize the top 4 principal components. Based on the interpretation of each
columns, what seems to distinguish capital cities with low vs. high values of
PC2?

```{r, fig.height = 4, fig.width = 8}
components <- tidy(pca_prep, 2)
library(glue)

components |>
  filter(component %in% glue("PC{1:4}")) |>
  ggplot() +
    geom_col(aes(terms, value)) +
    facet_grid(component ~ .) +
    theme(
      axis.title = element_text(size = 14),
      axis.text.x = element_text(size = 12)
    )
```

```{r}
lookup
```



c. Visualize the scores of each capital city with respect to the first two
principal components. Make sure to annotate cities with their names. Pick a city
on the graph and interpret its relative wage profile based on the principal
components.
    
```{r, fig.width = 8, fig.height = 5}
scores <- bake(pca_prep, living_wages)

ggplot(scores) +
  geom_hline(aes(yintercept = 0),width = 3) +
  geom_vline(aes(xintercept = 0), width = 3) +
  geom_text(aes(PC1, PC, label = city))

```
