---
title: "Improving an App"
output: html_document
---

```{r}
library(tidyverse)
library(tidytext)
library(topicmodels)
theme_set(theme_bw())
set.seed(1234)
```
    
[Hotel Reviews] In this problem, we will practice using Latent Dirichlet
Allocation to understand the topics that come up across [hotel reviews](https://github.com/krisrs1128/stat479_s22/blob/main/_slides/week11/exercises/reviews.csv?raw=true) from an
online database. We will also study whether there are certain topics that are
more common in positive vs. negative reviews.

a. Transform the raw reviews into a collection of per-review word counts.
Remove stopwords from across all lexicons in `tidytext::stop_words`.

```{r}
reviews <- read_csv("https://github.com/krisrs1128/stat479_s22/blob/main/_slides/week11/exercises/reviews.csv?raw=true") %>%
  slice_sample(n = 2500)  # using half the data for convenience

reviews_dtm <- reviews %>%
  unnest_tokens(word, Review) %>%
  filter(!(word %in% stop_words$word)) %>%
  count(document, word) %>%
  cast_dtm(document, word, n)
```

b. Convert the `data.frame` from (a) into a topic models Document-Term
matrix (i.e., an object of class `DocumentTermMatrix`). Fit an LDA model
with 8 topics to the prepared object.

```{r}
fit <- LDA(reviews_dtm, k = 8, control = list(seed = 1234))
fit
```

c. Create a Structure plot displaying the topic memberships for each review.
Sort reviews according to their order on a hierarchical clustering tree, and
facet documents according to hotel rating. Are there certain topics that appear
to be more common in negative vs. positive reviews? Manually inspect a few
reviews with high membership in these topics.


```{r}
head(round(fit@gamma, 3))
```
```{r}
memberships <- tidy(fit, matrix = "gamma") %>%
  left_join(reviews %>% mutate(document = as.character(document)))

ggplot(memberships) +
  geom_col(aes(gamma, document, col = as.factor(topic))) +
  facet_grid(Rating ~ .)
```


```{r}
hclust_result <- hclust(dist(fit@gamma))
document_order <- fit@documents[hclust_result$order]
memberships <- tidy(fit, matrix = "gamma") %>%
  left_join(reviews %>% mutate(document = as.character(document))) %>%
  mutate(document = factor(document, levels = document_order))

ggplot(memberships) +
  geom_col(
    aes(gamma, document, fill = as.factor(topic), col = as.factor(topic))
  ) +
  facet_grid(Rating ~ ., space = "free", scales = "free") +
  scale_x_continuous(expand = c(0, 0)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
```

```{r}
memberships %>%
  filter(topic == 1) %>%
  arrange(-gamma)
```

d. Using either a heatmap or faceted barplot, visualize the content of the
topics. Which terms distinguish the topics that are associated with more
negative vs. positive reviews?

```{r}
topics <- tidy(fit, matrix = "beta")

top_terms <- topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 70) %>%
  mutate(term = reorder_within(term, beta, topic))
```


```{r, fig.height = 9, fig.width = 4}
ggplot(top_terms) +
  geom_col(aes(beta, term, fill = as.factor(topic))) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```






