---
title: "Hotel Reviews"
output: html_document
---

```{r}
library(tidyverse)
library(tidytext)
library(topicmodels)
theme_set(theme_bw())
set.seed(1234)
```
    
[Hotel Reviews] In this problem, we will practice using Latent Dirichlet
Allocation to understand the topics that come up across [hotel reviews](https://github.com/krisrs1128/stat479_s22/blob/main/_slides/week11/exercises/reviews.csv?raw=true) from an
online database. We will also study whether there are certain topics that are
more common in positive vs. negative reviews.

a. Transform the raw reviews into a collection of per-review word counts.
Remove stopwords from across all lexicons in `tidytext::stop_words`.

```{r}
reviews <- read_csv("https://github.com/krisrs1128/stat992_f23/raw/main/activities/week12/reviews.csv") |>
  slice_sample(n = 2500)  # using half the data for convenience
```

b. Convert the `data.frame` from (a) into a topic models Document-Term
matrix (i.e., an object of class `DocumentTermMatrix`). Fit an LDA model
with 8 topics to the prepared object.


c. Create a Structure plot displaying the topic memberships for each review.
Sort reviews according to their order on a hierarchical clustering tree, and
facet documents according to hotel rating. Are there certain topics that appear
to be more common in negative vs. positive reviews? Manually inspect a few
reviews with high membership in these topics.


d. Using either a heatmap or faceted barplot, visualize the content of the
topics. Which terms distinguish the topics that are associated with more
negative vs. positive reviews?

