---
title: ""
output: html_document
---

```{r}
library(tidyverse)
library(tidymodels)
theme_set(theme_bw())
set.seed(1234)
```
    
This problem will study a dataset from MIT's [living wage
calculator](https://livingwage.mit.edu/). Each row in this
[dataset](https://raw.githubusercontent.com/krisrs1128/stat479_s22/main/_slides/week10/exercises/living_wages.csv)
gives living wages for state capitals within the continental US. Since living
wages depend on a personal situation (e.g., number of children), this dataset is
high-dimensional. The interpretation of each column is 
[here](https://raw.githubusercontent.com/krisrs1128/stat479_s22/main/_slides/week10/exercises/living_wages_lookup.csv).


```{r}
living_wages <- read_csv("https://raw.githubusercontent.com/krisrs1128/stat479_s22/main/_slides/week10/exercises/living_wages.csv")
lookup <- read_csv("https://raw.githubusercontent.com/krisrs1128/stat479_s22/main/_slides/week10/exercises/living_wages_lookup.csv")
living_wages
```

a. Define a tidymodels `recipe` that normalizes all city features and
specifies that PCA should be performed.

b. Visualize the top 4 principal components. Based on the interpretation of each
columns, what seems to distinguish capital cities with low vs. high values of
PC2?

```{r, fig.height = 8.5}
```

c. Visualize the scores of each capital city with respect to the first two
principal components. Make sure to annotate cities with their names. Pick a city
on the graph and interpret its relative wage profile based on the principal
components.
    
```{r, eval = FALSE, fig.width = 10, fig.height = 5}
```
