---
title: "Improving an App"
output: html_document
---

```{r}
library(tidyverse)
library(tidytext)
library(topicmodels)
theme_set(theme_bw())
set.seed(1234)
```
    
[Hotel Reviews] In this problem, we will practice using Latent Dirichlet
Allocation to understand the topics that come up across [hotel reviews](https://github.com/krisrs1128/stat479_s22/blob/main/_slides/week11/exercises/reviews.csv?raw=true) from an
online database. We will also study whether there are certain topics that are
more common in positive vs. negative reviews.

a. Transform the raw reviews into a collection of per-review word counts.
Remove stopwords from across all lexicons in `tidytext::stopwords`.

```{r}
reviews <- read_csv("https://github.com/krisrs1128/stat479_s22/blob/main/_slides/week11/exercises/reviews.csv?raw=true") %>%
  slice_sample(n = 2500)

reviews_dtm <- reviews %>%
  unnest_tokens(word, Review) %>%
  filter(!(word %in% stop_words$word)) %>%
  count(document, word) %>%
  cast_dtm(document, word, n)
```

b. Convert the `data.frame` from (a) into a topic models Document-Term
matrix (i.e., an object of class `DocumentTermMatrix`). Fit an LDA model
with 8 topics to the prepared object.

```{r}
tic <- Sys.time()
fit <- LDA(reviews_dtm, k = 8, control = list(seed = 1234))
Sys.time() - tic
```

c. Create a Structure plot displaying the topic memberships for each review.
Sort reviews according to their order on a hierarchical clustering tree, and
facet documents according to hotel rating. Are there certain topics that appear
to be more common in negative vs. positive reviews? Manually inspect a few
reviews with high membership in these topics.

```{r}
hclust_result <- hclust(dist(fit@gamma))
document_order <- fit@documents[hclust_result$order]
memberships <- tidy(fit, matrix = "gamma") %>%
  left_join(reviews %>% mutate(document = as.character(document))) %>%
  mutate(document = factor(document, levels = document_order))
```

We can finally create a structure plot.

```{r, fig.height = 10, fig.width = 6}
ggplot(memberships) +
  geom_col(aes(gamma, document, fill = as.factor(topic), col = as.factor(topic))) +
  facet_grid(Rating ~ ., scale = "free", space = "free") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  theme(
    strip.text.y = element_text(angle = 0),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  )
```

```{r}
memberships %>% 
  filter(topic == 1) %>% 
  arrange(-gamma)
```

d. Using either a heatmap or faceted barplot, visualize the content of the
topics. Which terms distinguish the topics that are associated with more
negative vs. positive reviews?

```{r, fig.height = 18, fig.width = 7}
topics <- tidy(fit, matrix = "beta")

top_terms <- topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 70) %>%
  mutate(term = reorder_within(term, beta, topic))

ggplot(top_terms, aes(sqrt(beta), term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_fill_brewer(palette = "Set2") +
  scale_y_reordered()
```

Bonus: This is outside the scope of this class, but if we wanted, we could even
fit a model to predict review rating just from the topic memberships.

```{r, eval = FALSE}
library(caret)

pd <- memberships %>%
  pivot_wider(names_from = "topic", values_from = "gamma") %>%
  select(Rating:8)
rf_fit <- train(x = pd %>% select(-Rating), y = as.factor(pd$Rating), method = "rf")
rf_fit # better than the 20% baseline

varImp(rf_fit)
```




