---
title: "Hotel Reviews"
output: html_document
---

```{r}
library(tidyverse)
library(tidytext)
library(topicmodels)
theme_set(theme_bw())
set.seed(1234)
```
    
[Hotel Reviews] In this problem, we will practice using Latent Dirichlet
Allocation to understand the topics that come up across [hotel reviews](https://github.com/krisrs1128/stat479_s22/blob/main/_slides/week11/exercises/reviews.csv?raw=true) from an
online database. We will also study whether there are certain topics that are
more common in positive vs. negative reviews.

a. Transform the raw reviews into a collection of per-review word counts.
Remove stopwords from across all lexicons in `tidytext::stop_words`.

```{r}
reviews <- read_csv("https://github.com/krisrs1128/stat992_f23/raw/main/activities/week12/reviews.csv") |>
  slice_sample(n = 2500)  # using half the data for convenience

reviews_dtm <- reviews |>
  unnest_tokens(word, Review) |>
  filter(!(word %in% stop_words$word)) |>
  count(document, word) |>
  cast_dtm(document, word, n)
```

b. Convert the `data.frame` from (a) into a topic models Document-Term
matrix (i.e., an object of class `DocumentTermMatrix`). Fit an LDA model
with 8 topics to the prepared object.

```{r}
fit <- LDA(reviews_dtm, k = 8, control = list(seed = 1234))
```


c. Create a Structure plot displaying the topic memberships for each review.
Sort reviews according to their order on a hierarchical clustering tree, and
facet documents according to hotel rating. Are there certain topics that appear
to be more common in negative vs. positive reviews? Manually inspect a few
reviews with high membership in these topics.

```{r}
leaf_order <- hclust(dist(fit@gamma))$order
gamma <- tidy(fit, "gamma") |>
  left_join(reviews |> mutate(document = as.factor(document))) |>
  mutate(document = factor(document, levels = fit@documents[leaf_order]))

ggplot(gamma) +
  geom_col(aes(document, gamma, fill = factor(topic), col = factor(topic))) +
  scale_y_continuous(expand = c(0, 0)) +
  facet_grid(. ~ Rating, scale = "free_x") +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text = element_text(size = 24)
  )


```


d. Using either a heatmap or faceted barplot, visualize the content of the
topics. Which terms distinguish the topics that are associated with more
negative vs. positive reviews?

```{r}
beta <- tidy(fit, "beta") |>
  group_by(topic) |>
  slice_max(beta, n = 40)

ggplot(beta) +
  geom_col(aes(beta, reorder_within(term, beta, topic), fill = factor(topic))) +
  scale_y_reordered() +
  facet_wrap(~ topic, scales = "free_y", ncol = 4)
```
