---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(mgcv)
library(ungeviz)
library(jsonlite)
theme_set(theme_bw())
```

1. [South African Heart Disease GAM] In this problem, we will visualize the
prediction uncertainty in a generalized additive model (GAM) of the South
African Heart Disease
[dataset](https://hastie.su.domains/ElemStatLearn/datasets/SAheart.info.txt).
This data were used to evaluate risk factors for heart disease in a sample of
462 South African men in a region with high coronary heart disease (CHD)
prevalence. We will use a GAM to fit a type of logistic regression to the binary
CHD response using LDL cholesterol level as the predictor. Unlike standard
logistic regression, a GAM's logistic regression does not constrain the
predicted probability to follow a logistic function^[This is achieved by applying the logistic link to a nonlinear transformation of LDL.].

a. Make a jittered scatterplot showing how CHD risk varies as a function of LDL.

```{r}
heart <- read_csv("https://github.com/krisrs1128/stat679_code/raw/main/activities/week13/heart.csv")
ggplot(heart) +
  geom_jitter(aes(ldl, chd), width = 0, height = 0.1)
```

b. The code below fits a GAM between LDL and CHD. Visualize 20 predicted
probability curves obtained by bootstrapping the original dataset.

```{r}
fit <- gam(chd ~ s(ldl), data = heart, family = "binomial")
new_data <- tibble(ldl = seq(min(heart$ldl), max(heart$ldl), length.out = 100))
sample_df <- sample_outcomes(fit, new_data, 20)

ggplot(heart, aes(ldl, chd)) +
  geom_jitter(width = 0, height = 0.1) +
  geom_line(data = sample_df, aes(group = .draw), alpha = 0.3)
```

c. Overlay a 95% pointwise confidence band onto the 20 hypothetical outcomes
from (b).

```{r}
conf <- confidence_band(fit, new_data, times = 100)
ggplot(heart, aes(ldl, chd)) +
  geom_jitter(width = 0, height = 0.1) +
  geom_ribbon(data = conf, aes(ymin = lo, ymax = hi), fill = "#d3d3d3", color = NA) +
  geom_line(data = sample_df, aes(group = .draw), alpha = 0.3)
```

d. Instead of showing all the predicted probability curves simultaneously,
create an animated hypothetical outcome plot. Each frame should highlight both
the a hypothetical predicted probability curve and the samples used to generate
that bootstrap sample.

```{r}
bootstrap_data <- function(df, newdata) {
  fit <- gam(chd ~ s(ldl), data = df, family = "binomial")
  y_hat <- predict(fit, newdata, type = "response")
  list(
    curve = data.frame(ldl = new_data$ldl, y_hat = y_hat),
    ids = df[[".original_id"]] - 1
  )
}

bootstrapper(100)(heart) %>%
  split(.$.draw) %>%
  map(~ bootstrap_data(., new_data)) %>%
  write_json("curves.json")

heart %>%
  write_csv("heart.csv")

conf %>%
  mutate(
    lo = as.numeric(lo),
    hi = as.numeric(hi)
  ) %>%
  select(ldl, lo, hi) %>%
  write_csv("conf.csv")
```
