---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(brms)
library(ggdist)
library(gganimate)
theme_set(theme_bw())
```

[Evolutionary Ecology] This problem visualizes the uncertainty of estimates
derived from an evolutionary ecology model. Vonesh and Bolker (2005) ran an
experiment to see how three factors -- size, initial population density, and
presence of predators -- influenced tadpole survival. There were several
replicate tanks for each combination of factors. As an initial analysis
strategy, it is natural to quantify the uncertainty in per-tank survival
probability using a multilevel model. This is discussed in full detail in
Chapter 12 of McElreath's [Statistical Rethinking](https://xcelab.net/rm/statistical-rethinking/)^[This book is accompanied by a fantastic set of [free lectures](https://www.youtube.com/playlist?list=PLDcUM9US4XdMROZ57-OIRtIK0aOynbgZN).].
This model implements a kind of partial pooling: Each tank is allowed to have
its own survival probability, but information is shared across all the tanks.

a. Each row in the raw dataset below describes a single tank. Visualize
variation in tank-level survival, as well as the potential influence of
initial density and tadpole size.
```{r}
x <- read_csv("https://raw.githubusercontent.com/krisrs1128/stat679_code/main/activities/week13/reedfrogs.csv") %>%
  mutate(tank = as.factor(tank))

ggplot(x) +
  geom_point(aes(propsurv, reorder(tank, propsurv), col = pred)) +
  facet_wrap(size ~ density, scale = "free_y")
```
  
b. The code below fits the following model, where $y_{i}$ represents the
number of tadpoles that survive in tank $i$, $N_{i}$ is the initial
tadpole density, and $p_{i}$ is the (unknown) survival probability.
    
\begin{align*}
y_{i} &\sim \text{Bin}\left(N_{i}, p_{i}\right) \\
p_{i} &= \text{logit}^{-1}\left(\alpha_{i}\right) \\
\alpha_{i} &\sim \mathcal{N}\left(0, 2\right)
\end{align*}
```{r, message = FALSE, warning = FALSE}
library(brms)
fit <- brm(
  data = x, family = binomial,
  surv | trials(density) ~ 0 + factor(tank),
  prior(normal(0, 2)),
  chains = 1
)

posterior <- as_draws_df(fit)
```
Make a graded confidence plot of the posterior $p_{i}$ associated with each
tank. Overlay the tank's original survival probability, and comment on how
uncertainty varies across experimental settings.

```{r}

posterior <- posterior %>%
  pivot_longer(matches("factortank"), names_to = "variable") %>%
  mutate(tank = str_extract(variable, "[0-9]+")) %>%
  select(.draw, tank, value) %>%
  mutate(prob = inv_logit_scaled(value))
  
```

```{r}
posterior <- posterior %>%
  left_join(x)
posterior
```


```{r, fig.width = 4, fig.height = 1.5}
ggplot(posterior, aes(y = reorder(tank, propsurv))) +
  stat_pointinterval(aes(prob, col = pred)) +
  geom_point(aes(propsurv), shape = 1) +
  facet_wrap(size ~ density, scale = "free_y")
```

c. Create a version of the same figure that shows the full posterior
densities, rather than simply their quantiles.

```{r, fig.width = 3, fig.height = 1.5}
ggplot(posterior, aes(y = reorder(tank, propsurv))) +
  stat_slab(aes(prob, col = pred, fill = pred), height = 4, col = "#d4d4d4", size = .5) +
  facet_wrap(size ~ density, scale = "free_y")
```

d. In assessment of more complex models, it is often interesting to
visualize samples simulated from the fitted model. If the simulation
captures the most salient aspects of the original data without simply
memorizing it, then we can have more faith in our model. Conversely, if
important features are not reflected, then we may need to refine the model.
The code below samples 4000 survival counts for each tank in the fitted
model.
    
```{r}
y_sim <- posterior_predict(fit) %>%
  as_tibble() %>%
  mutate(.draw = row_number()) %>%
  pivot_longer(-.draw, names_to = "tank", values_to = "count") %>%
  mutate(tank = str_remove(tank, "V")) %>%
  left_join(x)

y_sim %>%
  filter(.draw < 11) %>%
  ggplot() +
    stat_dots(aes(count, reorder(tank, propsurv), col = pred, fill = pred)) +
    facet_wrap(size ~ density, scale = "free")
```
  
Create a static visualization that shows the variation associated with 10 of
these 4000 hypothetical datasets.

e. Create an animated hypothetical outcome plot of the same data used in the
previous part.

```{r}
p <- y_sim %>%
  ggplot() +
    geom_point(aes(count, reorder(tank, propsurv), col = pred)) +
    facet_wrap(size ~ density, scale = "free") +
    transition_time(.draw)

anim_save("~/Downloads/animation.gif", p, renderer = gifski_renderer())
```


