---
title: "NYC Rentals"
output: html_document
---

```{r}
library(shiny)
library(glue)
library(bslib)
library(tidyverse)

# code to set a clean theme
th <- theme_minimal() + 
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "#F7F7F7"),
    panel.border = element_rect(fill = NA, color = "#0c0c0c", size = 0.6),
    axis.text = element_text(size = 14),
    axis.title = element_text(size = 16),
    legend.position = "bottom"
  )
theme_set(th)
```
    
[NYC Rentals] In this problem, we'll create a visualization to dynamically
query a
[dataset](https://uwmadison.box.com/shared/static/zi72ugnpku714rbqo2og9tv2yib5xped.csv)
of Airbnb rentals in Manhattan in 2019. The steps below guide you through the
process of building this visualization.

```{r}
rentals <- read_csv("https://uwmadison.box.com/shared/static/zi72ugnpku714rbqo2og9tv2yib5xped.csv") |>
  mutate(trunc_price = pmin(price, 1e3))
```

    
a. Make a scatterplot of locations (Longitude vs. Latitude) for all the rentals,
colored in by `room_type`.

b. Design a plot and a dynamic query so that clicking or brushing on the
plot updates the points that are highlighted in the scatterplot in (a). For
example, you may query a histogram of prices to focus on neighborhoods that
are more or less affordable.

c. Implement the reverse graphical query. That is, allow the user to update
the plot in (b) by brushing over the scatterplot in (a).

* We've arleady added some functions for the histogram and map, assuming that there is a column called `selected_` in the input data.frame saying whether the sample should be highlighted.
* We've already setup the UI, including all the brushes.

```{r}
scatterplot <- function(df, selected_) {
  df |>
    mutate(selected = selected_) |>
    ggplot() +
    geom_point(
      aes(
        longitude, latitude, col = room_type, 
        alpha = as.numeric(selected),
        size = as.numeric(selected)
      )
    ) +
    scale_alpha(range = c(0.1, .5), guide = "none") +
    scale_size(range = c(0.1, .9), guide = "none") +
    scale_color_brewer(palette = "Set2") +
    coord_fixed() +
    theme_void()
}

overlay_histogram <- function(df, selected_) {
  sub_df <- filter(df, selected_)
  ggplot(df, aes(trunc_price, fill = room_type)) +
    geom_histogram(alpha = 0.3, binwidth = 25) +
    geom_histogram(data = sub_df, binwidth = 25) +
    scale_y_continuous(expand = c(0, 0, 0.1, 0)) +
    scale_fill_brewer(palette = "Set2", guide = "none")
}

filter_df <- function(df, selected_) {
  filter(df, selected_) |>
    select(name, price, neighbourhood, number_of_reviews)
}

ui <- fluidPage(
  h3("NYC Airbnb Rentals"),
  fluidRow(
    column(6,
      plotOutput("histogram", brush = brushOpts("plot_brush", direction = "x"), height = 200),
      dataTableOutput("table")
    ),
    column(6, plotOutput("map", brush = "plot_brush", height = 600)),
  ),
  theme = bs_theme(bootswatch = "minty")
)

server <- function(input, output) {
  selected <- reactiveVal(rep(TRUE, nrow(rentals)))
  observeEvent(input$plot_brush, {
    selected(brushedPoints(rentals, input$plot_brush, allRows = TRUE)$selected_)
  })
  
  output$histogram <- renderPlot(overlay_histogram(rentals, selected()))
  output$map <- renderPlot(scatterplot(rentals, selected()))
  output$table <- renderDataTable(filter_df(rentals, selected()))
}

shinyApp(ui, server)
```


d. Comment on the resulting visualization(s). If you had a friend who was
interested in renting an Airbnb in NYC, what would you tell them?

